---
title: "01 Data Prep"
output: false
---
Replication workflow for:

"Ideological Bias in Estimates of the Impact of Immigration"

[George J. Borjas](https://www.hks.harvard.edu/faculty/george-borjas) <br>
[Nate Brezau](https://sites.google.com/site/nbreznau/) <br>

The original workflow was developed by Borjas using Stata (see `reg_model.do` in this repository), and this workflow is an identical set of analyses by Breznau done in R. 

The files `cri.csv` and `cri_team.csv` were generated in [Breznau, Rinke, Wuttke et al. 2022](https://www.pnas.org/doi/10.1073/pnas.2203150119) study, available in their [Github Repository](https://github.com/nbreznau/CRI). These data are supplemented from the original participant survey; public version available on the [Harvard Dataverse](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/UUP8CX).

## Setup

```{r setup}

packages <- c("tidyverse",
              "pacman",
              "here")

pacman::p_load(packages, character.only = T)

```

## Data

The files `cri_new_peer_scores.csv` (model-level peer review) and `peer_model_dyad.csv` (model-participant dyad scores) were generated from the R files in the folder `/data/data_prep/`: <br>
`001_subjective_voting_prep.R` <br>
`002_subjective_voting_indiv_model_dyads.R` <br>

These files rely on the original fourth wave of the participant survey `W4_export.sav` which has participant identifiers and therefore cannot be publicly shared.

```{r data}

cri <- read_csv(here("data", "cri.csv"))
cri_team <- read_csv(here("data", "cri_team.csv"))
peer_model_dyad <- read_csv(here("data", "peer_model_dyad.csv"))
cri_new_peer_scores <- read_csv(here("data", "cri_new_peer_scores.csv"))
df_dyad <- read_csv(here("data", "cri_long_participant_ame_dyad.csv"))
df_sem_p <- read_csv(here("data", "sem_p.csv")) %>%
  mutate(stats_i = stats,
         belief_i = belief,
         topic_i = topic) %>%
  dplyr::select(u_id, stats_i, topic_i, belief_i)

```

### Cleaning

Drop original study from Brady and Finnigan which the Breznau, Rinke, Wuttke et al. study was based on, remove missings and remove unused variables. 

```{r clean}
df <- cri %>%
  subset(u_teamid != 0 & !is.na(AME), select = -c(AU:VE, emigration_ivC:fbXleftright))

```


### What is the N?
The N is 158. But there is an error in the team_size variable from the original study. The error is that the team_size for teamid == 93 is currently 2, but actually there were 3, and the team_size for teamid == 94 is currently 2, but there was only 1. 

```{r cases}

# valid cases from the PIs
valid_id <- read_csv(here("data", "valid_ids.csv")) %>%
  subset(u_teamid %in% df$u_teamid)

team_size_check <- valid_id %>%
  group_by(u_teamid) %>%
  mutate(team_size_check = n()) %>%
  select(-u_id) %>%
  summarise_all(mean)

df <- df %>%
  left_join(team_size_check, by = "u_teamid")

df <- df %>%
  mutate(team_size_not_correct = ifelse(team_size - team_size_check == 0, 0, 1))

df$u_teamid[df$team_size_not_correct == 1]

df$team_size[df$u_teamid == 93]

df$team_size_check[df$u_teamid == 93]

df$team_size[df$u_teamid == 94]

df$team_size_check[df$u_teamid == 94]

# recode team_size to the correct sizes (two errors)
df <- df %>%
  mutate(team_size = ifelse(u_teamid == 93, 3,
                            ifelse(u_teamid == 94, 1, team_size)))

df_dyad <- df_dyad %>%
  mutate(team_size = ifelse(u_teamid == 93, 3,
                            ifelse(u_teamid == 94, 1, team_size)))

total_participants <- df %>%
  distinct(u_teamid, team_size) %>%
  summarise(total_participants = sum(team_size, na.rm = TRUE))

```

### Recoding

1. Generate percent of team that are male (impute 0.67 for the team with missing, see Borjas Stata explanation)
2. Generate implied standard error as ame/z
3. Generate degree combinations (see Stata code for logic)

Step 1: start with discipline of first author, the mdegree variable goes from 0 to 7 

Step 2: reset the value of mdegree to 20 if the team has 2 people with different disciplines

Step 3: reset the value of mdegree to 33 if the team has two sociologists, and a sociologist lead author
	reset the value to 34 if the team has two political scientists, and a political scientist lead author
	reset the value to 35 if the team has two sociologists, but a poli sci lead author
	reset the value to 36 if the team has two political scientists, but a sociology lead author
	reset the value to 40 if there is some other combination for 3-person teams 

This would be the code:

generate mdegree=degree1;
replace mdegree=0 if counter2==3005;
replace mdegree=20 if counter2==2204 | counter2==2306 | counter2==2504 | counter2==2703;
replace mdegree=33 if counter2==3323 | counter2==3336 | counter2==3343;
replace mdegree=34 if counter2==3414 | counter2==3443;
replace mdegree=35 if counter2==3433;
replace mdegree=36 if counter2==3344;
replace mdegree=40 if counter2==3244 | counter2==3654;

4. Generate pro-immigration and team-index
5. Generate topic_knowledge and stat_skill (impute one missing team, see Stata)
6. Generate belief in hypothesis variables


```{r recode}

df <- df %>%
  mutate(p1_male = case_when(v_1101 == 2 ~ 0,
                             .default = v_1101),
         p2_male = case_when(v_1102 == 2 ~ 0,
                             .default = v_1102),
         p3_male = case_when(v_1103 == 2 ~ 0,
                             .default = v_1103)) %>%
  rowwise() %>%
  mutate(nmale = sum(p1_male, p2_male, p3_male, na.rm = T)/team_size) %>%
  ungroup() %>%
  mutate(nmale = ifelse(u_teamid == 27, 0.6666667, nmale),
         std = AME/abs(z),
         d1 = ifelse(is.na(backgr_degree1), 0, as.numeric(backgr_degree1)),
         d2 = ifelse(is.na(backgr_degree2), 0, as.numeric(backgr_degree2)),
         d3 = ifelse(is.na(backgr_degree3), 0, as.numeric(backgr_degree3)),
         counter = d1*100 + d2*10 + d3,
         counter2 = team_size*1000 + counter,
         mdegree = backgr_degree1,
         mdegree = case_when(
           counter2 == 3005 ~ 0,
           counter2 == 2204 ~ 20,
           counter2 == 2306 ~ 20,
           counter2 == 2504 ~ 20,
           counter2 == 2703 ~ 20,
           counter2 == 3323 ~ 33,
           counter2 == 3336 ~ 33,
           counter2 == 3343 ~ 33,
           counter2 == 3414 ~ 34,
           counter2 == 3443 ~ 34,
           counter2 == 3433 ~ 35,
           counter2 == 3344 ~ 36,
           counter2 == 3654 ~ 40,
           counter2 == 3244 ~ 40,
           .default = mdegree),
         pro_index = pro_immigrant,
         att1 = 7 - attitude_immigration_11,
         att2 = 7 - attitude_immigration_12,
         att3 = 7 - attitude_immigration_13,
         team = rowSums(!is.na(across(c(att1, att2, att3)))),
         npro = (ifelse(!is.na(att1) & att1 > 4, 1, 0)) +
            (ifelse(!is.na(att2) & att2 > 4, 1, 0)) +
            (ifelse(!is.na(att3) & att3 > 4, 1, 0)),
         npro = ifelse(is.na(npro), 0, npro),
         pindex = npro/team,
         dindex = ifelse(pindex >= .5, 1, 0),
         att1 = ifelse(is.na(att1), 0, att1),
         att2 = ifelse(is.na(att2), 0, att2),
         att3 = ifelse(is.na(att3), 0, att3),
         npro1 = (ifelse(att1==1, 1, 0)) +
                 (ifelse(att2==1, 1, 0)) +
                 (ifelse(att3==1, 1, 0)),
         npro2 = (ifelse(att1==2, 1, 0)) +
                 (ifelse(att2==2, 1, 0)) +
                 (ifelse(att3==2, 1, 0)),
         npro3 = (ifelse(att1==3, 1, 0)) +
                 (ifelse(att2==3, 1, 0)) +
                 (ifelse(att3==3, 1, 0)),
         npro4 = (ifelse(att1==4, 1, 0)) +
                 (ifelse(att2==4, 1, 0)) +
                 (ifelse(att3==4, 1, 0)),
         npro5 = (ifelse(att1==5, 1, 0)) +
                 (ifelse(att2==5, 1, 0)) +
                 (ifelse(att3==5, 1, 0)),
         npro6 = (ifelse(att1==6, 1, 0)) +
                 (ifelse(att2==6, 1, 0)) +
                 (ifelse(att3==6, 1, 0)),
         npro1 = ifelse(is.na(npro1), 0, npro1),
         npro2 = ifelse(is.na(npro2), 0, npro2),
         npro3 = ifelse(is.na(npro3), 0, npro3),
         npro4 = ifelse(is.na(npro4), 0, npro4),
         npro5 = ifelse(is.na(npro5), 0, npro5),
         npro6 = ifelse(is.na(npro6), 0, npro6),
         p1 = npro1/team,
         p2 = npro2/team,
         p3 = npro3/team,
         p4 = npro4/team,
         p5 = npro5/team,
         p6 = npro6/team,
         p12 = p1+p2,
         p34 = p3+p4,
         p56 = p5+p6,
         group1 = ifelse(p12>0, 1, 0),
         group3 = ifelse(pindex>=.5, 1, 0),
         group3 = ifelse(group1==1 & group3==1, 1, group3),
         group1 = ifelse(group1==1 & group3==1, 0, group1),
         group2 = ifelse(group1==0 & group3==0, 1, 0),
         group1 = ifelse(is.na(group1), 0, group1),
         group2 = ifelse(is.na(group2), 0, group2),
         group3 = ifelse(is.na(group3), 0, group3),
         index = 1*group1 + 2*group2 + 3*group3,
         topic_knowledge = ifelse(u_teamid==27, "Low", TOPIC_KNOWLEDGE),
         topic_ipred = ifelse(u_teamid == 27, -0.253722245526001, topic_ipred),
         topic_cat = case_match(topic_knowledge,
                                "Low" ~ 1,
                                "Mid" ~ 2,
                                "High" ~ 3),
         topic_brw = (topic_ipred - mean(topic_ipred)) / sd(topic_ipred), # standardize
         statistics_skill = ifelse(u_teamid == 27, "Mid", STATISTICS_SKILL),
         stats_ipred = ifelse(u_teamid == 27, 0.102538885683808, stats_ipred),
         stats_cat = case_match(statistics_skill,
                                "Low" ~ 1,
                                "Mid" ~ 2,
                                "High" ~ 3),
         stats_brw = ifelse(u_teamid == 8, 0.649019158901927, stats_ipred),
         stats_brw = (stats_brw - mean(stats_brw)) / sd(stats_brw), # standardize
         model_cat = case_match(MODEL_SCORE,
                               "Low" ~ 1,
                               "Mid" ~ 2,
                               "High" ~ 3),
         model_brw = total_score,
         quality = case_match(MODEL_SCORE,
                              "High" ~ 1,
                              .default = 0),
         belief_hypothesis = ifelse(u_teamid == 27, "Low", BELIEF_HYPOTHESIS),
         belief_ipred = ifelse(u_teamid == 27, -1.13508799270782, belief_ipred),
         belief_cat = case_match(belief_hypothesis,
                                 "Low" ~ 1,
                                 "Mid" ~ 2,
                                 "High" ~ 3),
         teamx = (ifelse(is.na(belief_H1_11), 0, 1)) +
           (ifelse(is.na(belief_H1_12), 0, 1)) +
           (ifelse(is.na(belief_H1_13), 0, 1)),
         nbelief = (ifelse(is.na(belief_H1_11), 0, ifelse(belief_H1_11 <= 2, 1, 0))) +
                      (ifelse(is.na(belief_H1_12), 0, ifelse(belief_H1_12 <= 2, 1, 0))) +
                      (ifelse(is.na(belief_H1_13), 0, ifelse(belief_H1_13 <= 2, 1, 0))),
         pbelief = nbelief/teamx,
         dep = as.factor(DV)
         
  )

```

### Merge Peer Review

The new scores generated here in data/data_prep.

Generate variable for high peer review

```{r npr}

df2 <- df %>%
  left_join(cri_new_peer_scores, by = "id") %>%
  mutate(
    quality2 = case_when(
      peer_mean > 4.5 ~ 1,
      peer_mean <= 4.5 ~ 0,
      .default = NA)
  )
  
```

### Impute Peer Scores

```{r imp}

m_imp <- lm(peer_mean ~ model_brw + Jobs + Unemp + IncDiff + OldAge + House + Health + logit + ols + Stock + Flow + ChangeFlow + w1985 + w1990 + w1996 + w2006 + w2016 + orig13 + eeurope + allavailable + twowayfe + level_cyear + mlm_fe + mlm_re + anynonlin, data = df2)

df2$phat <- predict(m_imp, newdata = df2)

df2 <- df2 %>%
  mutate(pscore = ifelse(is.na(peer_mean), phat, peer_mean))

```

### Create 10% cuts

```{r c10}
df2 <- df2 %>%
  # add in variables for distributional analyses
  mutate(negsig = ifelse(AME < 0 & abs(z) > 1.645, 1, 0),
         possig = ifelse(AME > 0 & abs(z) > 1.645, 1, 0),
         pos10 = ifelse(AME > .052, 1, 0),
         neg10 = ifelse(AME < -.071, 1, 0),
         pos10s = ifelse(AME > .052 & abs(z) > 1.645, 1, 0),
         neg10s = ifelse(AME < -.071 & abs(z) > 1.645, 1, 0),
         highstats = ifelse(statistics_skill == "High", 1, 0),
         hightopic = ifelse(topic_knowledge == "High", 1, 0),
         highmodel = ifelse(MODEL_SCORE == "High", 1, 0),
         proindex = pro_immigrant,
         t2 = case_when(team_size==1 ~ 1,
                        .default = 0),
         t3 = case_when(team_size==3 ~ 1,
                        .default = 0))

df2 <- df2 %>%
  group_by(u_teamid) %>%
  mutate(nmodel = n()) %>%
  ungroup()

pdiv <- (sum(df2$pscore)/1253)

df2 <- df2 %>%
  mutate(pscore_Z = (pscore - mean(pscore)) / sd(pscore),
         peer_mean_Z = peer_mean - mean(df2$peer_mean, na.rm = T),
         pscore_1 = pscore/(sum(df2$pscore)/1253)) # standardize & make a weighted to sum = 1 version
```

## Individual-level Dyads

We reproduce the data cleaning process on the individual level data here. Except degree, here we can just use their degree without collapsing to the team level.

These data also rely on sem_p.csv generated in the CRI workflow 002_CRI_Data_Prep.Rmd. It has the individual-level scores (in their original form, meaning that belief in the hypothesis is reversed). But it does not have them for all individuals, because of missing data (only N = 147)

```{r indivdyad}


# peer scores
df3 <- df_dyad %>%
  left_join(cri_new_peer_scores, by = "id")  %>% 
  subset(!is.na(AME))

df3 <- df3 %>%
  mutate(p1_male = case_when(v_1101 == 2 ~ 0,
                             .default = v_1101),
         p2_male = case_when(v_1102 == 2 ~ 0,
                             .default = v_1102),
         p3_male = case_when(v_1103 == 2 ~ 0,
                             .default = v_1103)) %>%
  rowwise() %>%
  mutate(nmale = sum(p1_male, p2_male, p3_male, na.rm = T)/team_size) %>%
  ungroup() %>%
  mutate(nmale = ifelse(u_teamid == 27, 0.6666667, nmale),
         std = AME/abs(z),
         # make factor to automatically drop moderate
         indiv = case_when(attitude_immigration_1 == 1 | attitude_immigration_1 == 2 ~ 2,
                           attitude_immigration_1 == 3 | attitude_immigration_1 == 4 ~ 1,
                           attitude_immigration_1 == 5 | attitude_immigration_1 == 6 ~ 3,
                           TRUE ~ NA_real_),
         topic_knowledge = ifelse(u_teamid==27, "Low", TOPIC_KNOWLEDGE),
         topic_ipred = ifelse(u_teamid == 27, -0.253722245526001, topic_ipred),
         topic_cat = case_match(topic_knowledge,
                                "Low" ~ 1,
                                "Mid" ~ 2,
                                "High" ~ 3),
         topic_brw = (topic_ipred - mean(topic_ipred)) / sd(topic_ipred), # standardize
         statistics_skill = ifelse(u_teamid == 27, "Mid", STATISTICS_SKILL),
         stats_ipred = ifelse(u_teamid == 27, 0.102538885683808, stats_ipred),
         stats_cat = case_match(statistics_skill,
                                "Low" ~ 1,
                                "Mid" ~ 2,
                                "High" ~ 3),
         stats_brw = ifelse(u_teamid == 8, 0.649019158901927, stats_ipred),
         stats_brw = (stats_brw - mean(stats_brw)) / sd(stats_brw), # standardize
         model_cat = case_match(MODEL_SCORE,
                               "Low" ~ 1,
                               "Mid" ~ 2,
                               "High" ~ 3),
         model_brw = total_score,
         quality = case_match(MODEL_SCORE,
                              "High" ~ 1,
                              .default = 0),
         beliefx = as.numeric(belief_H1_1),
         pbelief = ifelse(beliefx == 1 | beliefx == 2, 1, 0),
         dep = as.factor(DV)
  )

# impute peer
m_imp <- lm(peer_mean ~ model_brw + Jobs + Unemp + IncDiff + OldAge + House + Health + logit + ols + Stock + Flow + ChangeFlow + w1985 + w1990 + w1996 + w2006 + w2016 + orig13 + eeurope + allavailable + twowayfe + level_cyear + mlm_fe + mlm_re + anynonlin, data = df3)

df3$phat <- predict(m_imp, newdata = df3)

df3 <- df3 %>%
  mutate(pscore = ifelse(is.na(peer_mean), phat, peer_mean))

# join with data from factor analysis 
df3 <- df3 %>%
  mutate(pscore_Z = (pscore - mean(pscore)) / sd(pscore),
         peer_mean_Z = peer_mean - mean(df2$peer_mean, na.rm = T),
         pscore_1 = pscore/((sum(df3$pscore)/1253)))  %>% # standardize & make a weighted to sum = 1 version
  left_join(df_sem_p, by = "u_id")

# impute missings from grouped means
df3 <- df3 %>%
  group_by(backgr_degree, STATISTICS_SKILL) %>%
  mutate(statimp = mean(stats_i, na.rm = T))

df3 <- df3 %>%
  group_by(backgr_degree, TOPIC_KNOWLEDGE) %>%
  mutate(topicimp = mean(topic_i, na.rm = T))

df3 <- df3 %>%
  group_by(backgr_degree, BELIEF_HYPOTHESIS) %>%
  mutate(beliefimp = mean(belief_i, na.rm = T)) %>%
  ungroup()

df3 <- df3 %>%
  mutate(stats_i = ifelse(is.na(stats_i), statimp, stats_i),
         topic_i = ifelse(is.na(topic_i), topicimp, topic_i),
         belief_i = ifelse(is.na(belief_i), beliefimp, belief_i))

# make weighting variable 'model' the number of models per person now (rather than team)
df3 <- df3 %>%
  group_by(u_id) %>%
  mutate(nmodel = n()) %>%
  ungroup()


df3 <- df3 %>%
  # add in variables for distributional analyses
  mutate(negsig = ifelse(AME < 0 & abs(z) > 1.645, 1, 0),
         possig = ifelse(AME > 0 & abs(z) > 1.645, 1, 0),
         pos10 = ifelse(AME > .052, 1, 0),
         neg10 = ifelse(AME < -.071, 1, 0),
         pos10s = ifelse(AME > .052 & abs(z) > 1.645, 1, 0),
         neg10s = ifelse(AME < -.071 & abs(z) > 1.645, 1, 0),
         highstats = ifelse(statistics_skill == "High", 1, 0),
         hightopic = ifelse(topic_knowledge == "High", 1, 0),
         highmodel = ifelse(MODEL_SCORE == "High", 1, 0),
         proindex = pro_immigrant,
         t2 = case_when(team_size==2 ~ 1,
                        .default = 0),
         t3 = case_when(team_size==3 ~ 1,
                        .default = 0),
         att = 7-as.numeric(attitude_immigration_1))

# different weighting now
df3 <- df3 %>%
  mutate(indiv2 = ifelse(indiv == 1, 1, 0),
         indiv1 = ifelse(indiv == 3, 1, 0),
         indiv3 = ifelse(indiv == 2, 1, 0)) %>%
  group_by(u_id) %>%
  mutate(nmodel = n()) %>%
  ungroup() %>%
  subset(!is.na(indiv))

df3$pweight <- 1/(df3$nmodel*df3$team_size)

#INDIVIDUAL LEVEL INDICES WILL BE SET TO MISSING IF THEY ARE MISSING BASIC INFORMATION ON STATS & TOPIC;
#THIS AFFECTS TEAM 33, WHICH ALTHOUGH HAS TEAM_SIZE = 3, THERE IS ONLY ONE U_ID FOR THE TEAM because none of the members participated in the survey;
df3 <- df3 %>%
  mutate(stats_i = ifelse(u_teamid == 33, NA, stats_i),
         topic_i = ifelse(u_teamid == 33, NA, topic_i),
         belief_i = ifelse(u_teamid == 33, NA, belief_i))


```

## Save DF

In both RDS and csv formats, to be user friendly

```{r save}

write_rds(df2, here("data", "df.rds"))
write.csv(df2, here("data", "df.csv"), row.names = F)
write.csv(df3, here("data", "df_dyad.csv"), row.names = F)

```

## Citations

```{r cites}

packages %>%
  map(citation) %>%
  print(style = "text")

```

## Colophon

```{r colo}

sessionInfo()

```

