---
title: "01 Data Prep"
output: html_notebook
---
Replication workflow for:

"Ideological Bias in Estimates of the Impact of Immigration"

[George J. Borjas](https://www.hks.harvard.edu/faculty/george-borjas) <br>
[Nate Brezau](https://sites.google.com/site/nbreznau/) <br>

The original workflow was developed by Borjas using Stata, and this version is an identical set of analyses by Breznau in R. 

The files cri.csv and cri_team.csv were generated in [Breznau, Rinke, Wuttke et al. 2022](https://www.pnas.org/doi/10.1073/pnas.2203150119) study, available in their [Github Repository](https://github.com/nbreznau/CRI). These data are supplemented from the original participant survey; public version available on the [Harvard Dataverse](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/UUP8CX).

## Setup

```{r setup}

packages <- c("tidyverse",
              "pacman",
              "here")

pacman::p_load(packages, character.only = T)

```

## Data

The files cri_new_peer_scores.csv (model-level peer review) and peer_model_dyad.csv (model-participant dyad scores) were generated from the R files in the folder /data/data_prep/: <br>
001_subjective_voting_prep.R <br>
002_subjective_voting_indiv_model_dyads.R <br>

These files rely on the original fourth wave of the participant survey W4_export.sav which has participant identifiers and therefore cannot be publicly shared.


```{r data}

cri <- read_csv(here("data", "cri.csv"))
cri_team <- read_csv(here("data", "cri_team.csv"))
peer_model_dyad <- read_csv(here("data", "peer_model_dyad.csv"))
cri_new_peer_scores <- read_csv(here("data", "cri_new_peer_scores.csv"))

```

## Citations

```{r cites}

```

## Colophon

```{r colo}

sessionInfo()

```

