---
title: "02 Analyses"
output: html_notebook
---
Replication workflow for:

"Ideological Bias in Estimates of the Impact of Immigration"

[George J. Borjas](https://www.hks.harvard.edu/faculty/george-borjas) <br>
[Nate Brezau](https://sites.google.com/site/nbreznau/) <br>

The original workflow was developed by Borjas using Stata (see `reg_model.do` in this repository), and this workflow is an identical set of analyses by Breznau done in R. 

The file `df.rds` (also available as csv) was generated in the file `01_Data_Prep.Rmd`.

## Setup

```{r setup}

packages <- c("tidyverse",
              "knitr",
              "miceadds",
              "pacman",
              "here",
              #"jtools",
              #"sjPlot",
              "stringr",
              "sandwich",
              "clubSandwich",
              "lmtest",
              "haven",
              "margins",
              "numDeriv",
              "pscl",
              "mediation")

pacman::p_load(packages, character.only = T)

# function to get r-squared

r2ext <- function(model) {
  summary_output <- capture.output(summary(model))
  combined_output <- paste(summary_output, collapse = " ")
  r2_pattern <- "R\\^2\\s*[:=]\\s*(\\d+\\.\\d+|\\d+)"
  cleaned_output <- str_replace(combined_output, "R\\^2\\s*[:=]\\s*", "")
  first_number <- round(as.numeric(str_extract(cleaned_output, "\\d+\\.\\d+|\\d+")),3)
  return(first_number)
}

```

## Data

```{r save}

df <- read_rds(here("data", "df.rds"))
df_dyad <- read_csv(here("data", "df_dyad.csv")) 

# original dataset taken from Stata
# df_stata <- read_dta(here("data", "model.dta"))
# df_stata_i <- read_dta(here("data", "individual.dta")) %>%
#   mutate(t2 = ifelse(team_size == 2, 1, 0),
#          t3 = ifelse(team_size == 3, 1, 0))

# d1 <- dplyr::select(df_dyad, AME, indiv1, indiv3, att, stats_i, topic_i, pbelief, t2, t3)
# d2 <- dplyr::select(df_stata_i, ame, indiv1, indiv3, att, stats_i, topic_i, pbelief, t2, t3)
# cor(d1, use = "pairwise.complete.obs")
# cor(d2, use = "pairwise.complete.obs")

```

## Models per Team

```{r amedesc}

team_ame_counts <- df %>%
  group_by(u_teamid) %>%
  summarize(count_AME = n()) # Count the number of AME values per u_teamid

overall_summary <- team_ame_counts %>%
  summarize(mean_count = mean(count_AME),
            sd_count = sd(count_AME))

overall_summary
```

## Summary Stats

```{r tbl1}
tbl1_team <- df %>%
  dplyr::select(u_teamid, index, AME, neg10s, pos10s, proindex, dindex, p12, p34, p56, group1, group2, group3, pbelief,  nmodel, 
	stats_brw, topic_brw, model_brw, team_size, peer_mean, quality, quality2, Hrej, pscore_Z) %>%
  group_by(u_teamid) %>%
  summarise_all(., mean, na.rm = T) %>%
  dplyr::select(-u_teamid) %>%
  ungroup()

tbl1_model <- df %>%
  dplyr::select(index, AME, neg10s, pos10s, group1, group2, group3, pbelief,  nmodel,  stats_brw, topic_brw, model_brw, team_size, pscore_Z, quality, quality2, Hrej, pscore)

tbl1_model_w <- df %>%
  dplyr::select(index, team_size, AME, neg10s, pos10s, nmodel)

tbl_5_model <- df %>% 
  dplyr::select(index, Scale, Stock, Flow, level_cyear, allavailable, w1996, w2006, w2016)
```

## Table 1

### T1 Model Level

```{r tbl1_model, warning = F}
n1 <- length(tbl1_model$index)
n2 <- length(tbl1_model$index[tbl1_model$index == 1])
n3 <- length(tbl1_model$index[tbl1_model$index == 2])
n4 <- length(tbl1_model$index[tbl1_model$index == 3])

mean1 <- tbl1_model %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "All teams")

mean2 <- tbl1_model %>%
  filter(index == 1) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Anti-imm")

mean3 <- tbl1_model %>%
  filter(index == 2) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Moderate")

mean4 <- tbl1_model %>%
  filter(index == 3) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Pro-imm")

Table_1_model <- bind_rows(mean1, mean2, mean3, mean4) %>%
  pivot_longer(cols = -sample, names_to = "Variable", values_to = "Mean") %>%
  pivot_wider(names_from = sample, values_from = Mean)

Table_1_model[,2:5] <- round(Table_1_model[,2:5], 3)

x <- as.data.frame(t(c("Num of teams",
                            length(tbl1_team$AME),
                            sum(tbl1_team$group1 == 1),
                            sum(tbl1_team$group2 == 1),
                            sum(tbl1_team$group3 == 1)
                            )))

colnames(x) <- colnames(Table_1_model)

Table_1_model <- rbind(x, Table_1_model)

Table_1_model$`All teams` <- as.numeric(Table_1_model$`All teams`)
Table_1_model$`Anti-imm` <- as.numeric(Table_1_model$`Anti-imm`)
Table_1_model$Moderate <- as.numeric(Table_1_model$Moderate)
Table_1_model$`Pro-imm` <- as.numeric(Table_1_model$`Pro-imm`)
  
Table_1_model[2:4,2] <- formatC(Table_1_model[2:4,2], format = "f", digits = 3)
Table_1_model[2:4,3] <- formatC(Table_1_model[2:4,3], format = "f", digits = 3)
Table_1_model[2:4,4] <- formatC(Table_1_model[2:4,4], format = "f", digits = 3)
Table_1_model[2:4,5] <- formatC(Table_1_model[2:4,5], format = "f", digits = 3)

# for visualizations (includes num of teams on top)
saveRDS(Table_1_model, here("results", "Table_1_model.rds"))

# for tables, removes num of teams on top
Table_1_model <- Table_1_model[2:20,]



```

##### T1 Model Level - Weighted

```{r tbl1_model_w, warning = F}
mean1 <- tbl1_model_w %>%
  summarise(across(-index, ~ weighted.mean(.x, w = 1 / nmodel, na.rm = TRUE))) %>%
  mutate(sample = "All teams")

mean2 <- tbl1_model_w %>%
  filter(index == 1) %>%
  summarise(across(-index, ~ weighted.mean(.x, w = 1 / nmodel, na.rm = TRUE))) %>%
  mutate(sample = "Anti-imm")

mean3 <- tbl1_model_w %>%
  filter(index == 2) %>%
  summarise(across(-index, ~ weighted.mean(.x, w = 1 / nmodel, na.rm = TRUE))) %>%
  mutate(sample = "Moderate")

mean4 <- tbl1_model_w %>%
  filter(index == 3) %>%
  summarise(across(-index, ~ weighted.mean(.x, w = 1 / nmodel, na.rm = TRUE))) %>%
  mutate(sample = "Pro-imm")

Table_1_model_w <- bind_rows(mean1, mean2, mean3, mean4) %>%
  pivot_longer(cols = -sample, names_to = "Variable", values_to = "Mean") %>%
  pivot_wider(names_from = sample, values_from = Mean)

Table_1_model_w[,2:5] <- round(Table_1_model_w[,2:5], 3)

Table_1_model_w <- as.data.frame(Table_1_model_w)

Table_1_model_w[1, 1:5] <- c("Num of teams",
                            length(tbl1_team$AME),
                            sum(tbl1_team$group1 == 1),
                            sum(tbl1_team$group2 == 1),
                            sum(tbl1_team$group3 == 1)
                            )

saveRDS(Table_1_model_w, here("results", "Table_1_model_w.rds"))
```

##### T1 Team Level

```{r tbl1_team}
nm1 <- length(tbl1_team$index)
nm2 <- length(tbl1_team$index[tbl1_team$index == 1])
nm3 <- length(tbl1_team$index[tbl1_team$index == 2])
nm4 <- length(tbl1_team$index[tbl1_team$index == 3])

mean1 <- tbl1_team %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "All teams")

mean2 <- tbl1_team %>%
  filter(index == 1) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Anti-imm")

mean3 <- tbl1_team %>%
  filter(index == 2) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Moderate")

mean4 <- tbl1_team %>%
  filter(index == 3) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Pro-imm")

Table_1_team <- bind_rows(mean1, mean2, mean3, mean4) %>%
  pivot_longer(cols = -sample, names_to = "Variable", values_to = "Mean") %>%
  pivot_wider(names_from = sample, values_from = Mean)

Table_1_team[,2:5] <- round(Table_1_team[,2:5], 3)



```

##### Build Table

```{r buildt1}

Table_1 <- as.data.frame(matrix(nrow = 15, ncol = 5))

Table_1[,1] <- c("Variable", "Mean AME", "% AME negative and significant", "% AME positive and significant", "Mean immigration sentiment", "% Anti-immigration teams", "% Moderate teams", "% Pro-immigration teams", "% Believe hypothesis", "Statistical skills (Z)", "Topic experience (Z)", "Peer score (Z)", "Team size", "N models", "N teams")

Table_1[1,2:5] <- c("All teams", "Anti-imm", "Moderate", "Pro-imm")

# Model-level summaries
Table_1[2:4,2:5] <- Table_1_model[1:3,2:5]

# Team-level summaries
Table_1_team <- subset(Table_1_team, Variable %in% c("proindex", "group1", "group2", "group3", "pbelief", "stats_brw", "topic_brw", "team_size"))

Table_1[c(5:11,13),2:5] <- Table_1_team[,2:5]

Table_1[12,2:5] <- Table_1_model[14,2:5]
Table_1[14,2:5] <- c(n1, n2, n3, n4)
Table_1[15,2:5] <- c(nm1, nm2, nm3, nm4)

kable(Table_1, col.names = c("","","","",""))

write_csv(Table_1, here("results", "TableS1.csv"))

```
#### Table 5

```{r t5b}

mean1 <- tbl_5_model %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "All teams")

mean2 <- tbl_5_model %>%
  filter(index == 1) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Anti-imm")

mean3 <- tbl_5_model %>%
  filter(index == 2) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Moderate")

mean4 <- tbl_5_model %>%
  filter(index == 3) %>%
  summarise(across(-index, mean, na.rm = T)) %>%
  mutate(sample = "Pro-imm")

Table_5 <- bind_rows(mean1, mean2, mean3, mean4) %>%
  pivot_longer(cols = -sample, names_to = "Variable", values_to = "Mean") %>%
  pivot_wider(names_from = sample, values_from = Mean)

Table_5[,2:5] <- round(Table_5[,2:5], 3)

kable(Table_5, col.names = c("Design decision", "All teams", "Anti- immigration", "Moderate", "Pro- immigration"))
```


## Table 2. AME Model-Level

### Build Models

```{r t2rs}

m_1 <- lm.cluster(formula=AME ~ group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_2 <- lm.cluster(formula=AME ~ group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_3 <- lm.cluster(formula=AME ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_4 <- lm.cluster(formula=AME ~ group1 + group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_5 <- lm.cluster(formula=AME ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_6 <- lm.cluster(formula=AME ~ proindex + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)


p_1 <- lm.cluster(formula=AME ~ group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_2 <- lm.cluster(formula=AME ~ group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_3 <- lm.cluster(formula=AME ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_4 <- lm.cluster(formula=AME ~ group1 + group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_5 <- lm.cluster(formula=AME ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_6 <- lm.cluster(formula=AME ~ proindex + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

null_m <- lm.cluster(formula=AME ~ stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

null_p <- lm.cluster(formula=AME ~ stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

# re-run as lm's to get fit stats
source(here("code", "Sub", "t2_fit.R"))

```

### Build Table

```{r t2r}

Table_2 <- as.data.frame(matrix(nrow = 32, ncol = 8))

Table_2[,1] <- c("Variable", "Anti-immigration team", "", "Pro-immigration team", "", "Statistical skills", "", "Topic experience", "", "Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC",  "R-squared", "", "Anti-immigration team", "", "Pro-immigration team", "",  "Statistical skills", "", "Topic experience", "","Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC", "R-squared")

Table_2[1,2:8] <- c("Null", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)")

#m_ models
Table_2[c(6,8),2] <- format(round(as.numeric(null_m$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_2[c(7,9),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_m)[2:3,2]),3), nsmall = 3))

Table_2[c(4,6,8),3] <- format(round(as.numeric(m_1$lm_res$coefficients[2:4]),3))
Table_2[c(5,7,9),3] <- sprintf("(%s)", format(round(as.numeric(summary(m_1)[2:4,2]),3), nsmall = 3))

Table_2[c(4,10,6,8),4] <- format(round(as.numeric(m_2$lm_res$coefficients[2:5]),3))
Table_2[c(5,11,7,9),4] <- sprintf("(%s)", format(round(as.numeric(summary(m_2)[2:5,2]),3), nsmall = 3))

Table_2[c(2,4,6,8),5] <- format(round(as.numeric(m_3$lm_res$coefficients[2:5]),3))
Table_2[c(3,5,7,9),5] <- sprintf("(%s)", format(round(as.numeric(summary(m_3)[2:5,2]),3), nsmall = 3))

Table_2[c(2,4,6,8,10),6] <- format(round(as.numeric(m_4$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_2[c(3,5,7,9,11),6] <- sprintf("(%s)", format(round(as.numeric(summary(m_4)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_2[c(12,6,8),7] <- format(round(as.numeric(m_5$lm_res$coefficients[2:4]), 3))
Table_2[c(13,7,9),7] <- sprintf("(%s)", format(round(as.numeric(summary(m_5)[2:4,2]),3), nsmall = 3))

Table_2[c(12,10,6,8),8] <- format(round(as.numeric(m_6$lm_res$coefficients[2:5]),3))
Table_2[c(13,11,7,9),8] <- sprintf("(%s)", format(round(as.numeric(summary(m_6)[2:5,2]),3), nsmall = 3))


Table_2[16,2:8] <- c(r2ext(null_m), r2ext(m_1), r2ext(m_2), r2ext(m_3), r2ext(m_4), r2ext(m_5), r2ext(m_6))

Table_2[14,2:8] <- round(c(logLik((null_ml)), logLik(m_1l), logLik(m_2l), logLik(m_3l), logLik(m_4l), logLik(m_5l), logLik(m_6l)),2)

Table_2[15,2:8] <- round(c(AIC((null_ml)), AIC(m_1l), AIC(m_2l), AIC(m_3l), AIC(m_4l), AIC(m_5l), AIC(m_6l)),2)

#p_ models
Table_2[c(22,24),2] <- format(round(as.numeric(null_p$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_2[c(23,25),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_p)[2:3,2]),3), nsmall = 3))

Table_2[c(20,22,24),3] <- format(round(as.numeric(p_1$lm_res$coefficients[2:4]),3))
Table_2[c(21,23,25),3] <- sprintf("(%s)", format(round(as.numeric(summary(p_1)[2:4,2]),3), nsmall = 3))

Table_2[c(20,26,22,24),4] <- format(round(as.numeric(p_2$lm_res$coefficients[2:5]),3))
Table_2[c(21,27,23,25),4] <- sprintf("(%s)", format(round(as.numeric(summary(p_2)[2:5,2]),3), nsmall = 3))

Table_2[c(18,20,22,24),5] <- format(round(as.numeric(p_3$lm_res$coefficients[2:5]),3))
Table_2[c(19,21,23,25),5] <- sprintf("(%s)", format(round(as.numeric(summary(p_3)[2:5,2]),3), nsmall = 3))

Table_2[c(18,20,22,24,26),6] <- format(round(as.numeric(p_4$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_2[c(19,21,23,25,27),6] <- sprintf("(%s)", format(round(as.numeric(summary(p_4)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_2[c(28,22,24),7] <- format(round(as.numeric(p_5$lm_res$coefficients[2:4]), 3))
Table_2[c(29,23,25),7] <- sprintf("(%s)", format(round(as.numeric(summary(p_5)[2:4,2]),3), nsmall = 3))

Table_2[c(28,26,22,24),8] <- format(round(as.numeric(p_6$lm_res$coefficients[2:5]),3))
Table_2[c(29,27,23,25),8] <- sprintf("(%s)", format(round(as.numeric(summary(p_6)[2:5,2]),3), nsmall = 3))

Table_2[32,2:8] <- c(r2ext(null_p), r2ext(p_1), r2ext(p_2), r2ext(p_3), r2ext(p_4), r2ext(p_5), r2ext(p_6))

Table_2[30,2:8] <- round(c(logLik((null_pl)), logLik(p_1l), logLik(p_2l), logLik(p_3l), logLik(p_4l), logLik(p_5l), logLik(p_6l)),2)

Table_2[31,2:8] <- round(c(AIC((null_pl)), AIC(p_1l), AIC(p_2l), AIC(p_3l), AIC(p_4l), AIC(p_5l), AIC(p_6l)),2)

Table_2[is.na(Table_2)] <- ""

write.csv(Table_2, here::here("results", "TableS2.csv"), row.names = F)

kable(Table_2, col.names = c("","","","","","","",""))


```

## Table 3. AME. Indiv-Model Dyads

Individual level models

### Build Models


```{r T3}

m_1d <- lm.cluster(formula=AME ~ indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_2d <- lm.cluster(formula=AME ~ indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_3d <- lm.cluster(formula=AME ~ indiv1 + indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_4d <- lm.cluster(formula=AME ~ indiv1 + indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_5d <- lm.cluster(formula=AME ~ att + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_6d <- lm.cluster(formula=AME ~ att + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)


p_1d <- lm.cluster(formula=AME ~ indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_2d <- lm.cluster(formula=AME ~ indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_3d <- lm.cluster(formula=AME ~ indiv1 + indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_4d <- lm.cluster(formula=AME ~ indiv1 + indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_5d <- lm.cluster(formula=AME ~ att + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_6d <- lm.cluster(formula=AME ~ att + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

null_md <- lm.cluster(formula=AME ~ stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

null_pd <- lm.cluster(formula=AME ~ stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

# re-run as lm's to get fit stats
source(here("code", "Sub", "t3_fit.R"))

#nobs(m_1ld)
```

### Build Table

```{r t3r}

Table_3 <- as.data.frame(matrix(nrow = 32, ncol = 8))

Table_3[,1] <- c("Variable", "Anti-immigration team", "", "Pro-immigration team", "", "Statistical skills", "", "Topic experience", "", "Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC",  "R-squared", "", "Anti-immigration team", "", "Pro-immigration team", "",  "Statistical skills", "", "Topic experience", "","Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC", "R-squared")

Table_3[1,2:8] <- c("Null", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)")

#m_ models
Table_3[c(6,8),2] <- format(round(as.numeric(null_md$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_3[c(7,9),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_md)[2:3,2]),3), nsmall = 3))

Table_3[c(4,6,8),3] <- format(round(as.numeric(m_1d$lm_res$coefficients[2:4]),3))
Table_3[c(5,7,9),3] <- sprintf("(%s)", format(round(as.numeric(summary(m_1d)[2:4,2]),3), nsmall = 3))

Table_3[c(4,10,6,8),4] <- format(round(as.numeric(m_2d$lm_res$coefficients[2:5]),3))
Table_3[c(5,11,7,9),4] <- sprintf("(%s)", format(round(as.numeric(summary(m_2d)[2:5,2]),3), nsmall = 3))

Table_3[c(2,4,6,8),5] <- format(round(as.numeric(m_3d$lm_res$coefficients[2:5]),3))
Table_3[c(3,5,7,9),5] <- sprintf("(%s)", format(round(as.numeric(summary(m_3d)[2:5,2]),3), nsmall = 3))

Table_3[c(2,4,6,8,10),6] <- format(round(as.numeric(m_4d$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_3[c(3,5,7,9,11),6] <- sprintf("(%s)", format(round(as.numeric(summary(m_4d)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_3[c(12,6,8),7] <- format(round(as.numeric(m_5d$lm_res$coefficients[2:4]), 3))
Table_3[c(13,7,9),7] <- sprintf("(%s)", format(round(as.numeric(summary(m_5d)[2:4,2]),3), nsmall = 3))

Table_3[c(12,10,6,8),8] <- format(round(as.numeric(m_6d$lm_res$coefficients[2:5]),3))
Table_3[c(13,11,7,9),8] <- sprintf("(%s)", format(round(as.numeric(summary(m_6d)[2:5,2]),3), nsmall = 3))


Table_3[16,2:8] <- c(r2ext(null_md), r2ext(m_1d), r2ext(m_2d), r2ext(m_3d), r2ext(m_4d), r2ext(m_5d), r2ext(m_6d))

Table_3[14,2:8] <- round(c(logLik((null_mld)), logLik(m_1ld), logLik(m_2ld), logLik(m_3ld), logLik(m_4ld), logLik(m_5ld), logLik(m_6ld)),2)

Table_3[15,2:8] <- round(c(AIC((null_mld)), AIC(m_1ld), AIC(m_2ld), AIC(m_3ld), AIC(m_4ld), AIC(m_5ld), AIC(m_6ld)),2)

#p_ models
Table_3[c(22,24),2] <- format(round(as.numeric(null_pd$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_3[c(23,25),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_pd)[2:3,2]),3), nsmall = 3))

Table_3[c(20,22,24),3] <- format(round(as.numeric(p_1d$lm_res$coefficients[2:4]),3))
Table_3[c(21,23,25),3] <- sprintf("(%s)", format(round(as.numeric(summary(p_1d)[2:4,2]),3), nsmall = 3))

Table_3[c(20,26,22,24),4] <- format(round(as.numeric(p_2d$lm_res$coefficients[2:5]),3))
Table_3[c(21,27,23,25),4] <- sprintf("(%s)", format(round(as.numeric(summary(p_2d)[2:5,2]),3), nsmall = 3))

Table_3[c(18,20,22,24),5] <- format(round(as.numeric(p_3d$lm_res$coefficients[2:5]),3))
Table_3[c(19,21,23,25),5] <- sprintf("(%s)", format(round(as.numeric(summary(p_3d)[2:5,2]),3), nsmall = 3))

Table_3[c(18,20,22,24,26),6] <- format(round(as.numeric(p_4d$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_3[c(19,21,23,25,27),6] <- sprintf("(%s)", format(round(as.numeric(summary(p_4d)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_3[c(28,22,24),7] <- format(round(as.numeric(p_5d$lm_res$coefficients[2:4]), 3))
Table_3[c(29,23,25),7] <- sprintf("(%s)", format(round(as.numeric(summary(p_5d)[2:4,2]),3), nsmall = 3))

Table_3[c(28,26,22,24),8] <- format(round(as.numeric(p_6d$lm_res$coefficients[2:5]),3))
Table_3[c(29,27,23,25),8] <- sprintf("(%s)", format(round(as.numeric(summary(p_6d)[2:5,2]),3), nsmall = 3))

Table_3[32,2:8] <- c(r2ext(null_pd), r2ext(p_1d), r2ext(p_2d), r2ext(p_3d), r2ext(p_4d), r2ext(p_5d), r2ext(p_6d))

Table_3[30,2:8] <- round(c(logLik((null_pld)), logLik(p_1ld), logLik(p_2ld), logLik(p_3ld), logLik(p_4ld), logLik(p_5ld), logLik(p_6ld)),2)

Table_3[31,2:8] <- round(c(AIC((null_pld)), AIC(p_1ld), AIC(p_2ld), AIC(p_3ld), AIC(p_4ld), AIC(p_5ld), AIC(p_6ld)),2)

Table_3[is.na(Table_3)] <- ""

write.csv(Table_3, here::here("results", "TableS3.csv"), row.names = F)

kable(Table_3, col.names = c("","","","","","","",""))


```


## Table 4. Neg Extreme. Model-level

### T4 LPMs

#### Build Models

```{r t4}

m_1n <- lm.cluster(formula=neg10s ~ group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_2n <- lm.cluster(formula=neg10s ~ group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_3n <- lm.cluster(formula=neg10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_4n <- lm.cluster(formula=neg10s ~ group1 + group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_5n <- lm.cluster(formula=neg10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_6n <- lm.cluster(formula=neg10s ~ proindex + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)


p_1n <- lm.cluster(formula=neg10s ~ group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_2n <- lm.cluster(formula=neg10s ~ group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_3n <- lm.cluster(formula=neg10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_4n <- lm.cluster(formula=neg10s ~ group1 + group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_5n <- lm.cluster(formula=neg10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_6n <- lm.cluster(formula=neg10s ~ proindex + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

null_mn <- lm.cluster(formula=neg10s ~ stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

null_pn <- lm.cluster(formula=neg10s ~ stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

# re-run as lm's to get fit stats
source(here("code", "Sub", "t4_fit.R"))

```

#### Build Table

```{r t4r}

Table_4 <- as.data.frame(matrix(nrow = 32, ncol = 8))

Table_4[,1] <- c("Variable", "Anti-immigration team", "", "Pro-immigration team", "", "Statistical skills", "", "Topic experience", "", "Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC",  "R-squared", "", "Anti-immigration team", "", "Pro-immigration team", "",  "Statistical skills", "", "Topic experience", "","Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC", "R-squared")

Table_4[1,2:8] <- c("Null", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)")

#m_ models
Table_4[c(6,8),2] <- format(round(as.numeric(null_mn$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_4[c(7,9),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_mn)[2:3,2]),3), nsmall = 3))

Table_4[c(4,6,8),3] <- format(round(as.numeric(m_1n$lm_res$coefficients[2:4]),3))
Table_4[c(5,7,9),3] <- sprintf("(%s)", format(round(as.numeric(summary(m_1n)[2:4,2]),3), nsmall = 3))

Table_4[c(4,10,6,8),4] <- format(round(as.numeric(m_2n$lm_res$coefficients[2:5]),3))
Table_4[c(5,11,7,9),4] <- sprintf("(%s)", format(round(as.numeric(summary(m_2n)[2:5,2]),3), nsmall = 3))

Table_4[c(2,4,6,8),5] <- format(round(as.numeric(m_3n$lm_res$coefficients[2:5]),3))
Table_4[c(3,5,7,9),5] <- sprintf("(%s)", format(round(as.numeric(summary(m_3n)[2:5,2]),3), nsmall = 3))

Table_4[c(2,4,6,8,10),6] <- format(round(as.numeric(m_4n$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_4[c(3,5,7,9,11),6] <- sprintf("(%s)", format(round(as.numeric(summary(m_4n)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_4[c(12,6,8),7] <- format(round(as.numeric(m_5n$lm_res$coefficients[2:4]), 3))
Table_4[c(13,7,9),7] <- sprintf("(%s)", format(round(as.numeric(summary(m_5n)[2:4,2]),3), nsmall = 3))

Table_4[c(12,10,6,8),8] <- format(round(as.numeric(m_6n$lm_res$coefficients[2:5]),3))
Table_4[c(13,11,7,9),8] <- sprintf("(%s)", format(round(as.numeric(summary(m_6n)[2:5,2]),3), nsmall = 3))


Table_4[16,2:8] <- c(r2ext(null_mn), r2ext(m_1n), r2ext(m_2n), r2ext(m_3n), r2ext(m_4n), r2ext(m_5n), r2ext(m_6n))

Table_4[14,2:8] <- round(c(logLik((null_mln)), logLik(m_1ln), logLik(m_2ln), logLik(m_3ln), logLik(m_4ln), logLik(m_5ln), logLik(m_6ln)),2)

Table_4[15,2:8] <- round(c(AIC((null_mln)), AIC(m_1ln), AIC(m_2ln), AIC(m_3ln), AIC(m_4ln), AIC(m_5ln), AIC(m_6ln)),2)

#p_ models
Table_4[c(22,24),2] <- format(round(as.numeric(null_pn$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_4[c(23,25),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_pn)[2:3,2]),3), nsmall = 3))

Table_4[c(20,22,24),3] <- format(round(as.numeric(p_1n$lm_res$coefficients[2:4]),3))
Table_4[c(21,23,25),3] <- sprintf("(%s)", format(round(as.numeric(summary(p_1n)[2:4,2]),3), nsmall = 3))

Table_4[c(20,26,22,24),4] <- format(round(as.numeric(p_2n$lm_res$coefficients[2:5]),3))
Table_4[c(21,27,23,25),4] <- sprintf("(%s)", format(round(as.numeric(summary(p_2n)[2:5,2]),3), nsmall = 3))

Table_4[c(18,20,22,24),5] <- format(round(as.numeric(p_3n$lm_res$coefficients[2:5]),3))
Table_4[c(19,21,23,25),5] <- sprintf("(%s)", format(round(as.numeric(summary(p_3n)[2:5,2]),3), nsmall = 3))

Table_4[c(18,20,22,24,26),6] <- format(round(as.numeric(p_4n$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_4[c(19,21,23,25,27),6] <- sprintf("(%s)", format(round(as.numeric(summary(p_4n)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_4[c(28,22,24),7] <- format(round(as.numeric(p_5n$lm_res$coefficients[2:4]), 3))
Table_4[c(29,23,25),7] <- sprintf("(%s)", format(round(as.numeric(summary(p_5n)[2:4,2]),3), nsmall = 3))

Table_4[c(28,26,22,24),8] <- format(round(as.numeric(p_6n$lm_res$coefficients[2:5]),3))
Table_4[c(29,27,23,25),8] <- sprintf("(%s)", format(round(as.numeric(summary(p_6n)[2:5,2]),3), nsmall = 3))

Table_4[32,2:8] <- c(r2ext(null_pn), r2ext(p_1n), r2ext(p_2n), r2ext(p_3n), r2ext(p_4n), r2ext(p_5n), r2ext(p_6n))

Table_4[30,2:8] <- round(c(logLik((null_pln)), logLik(p_1ln), logLik(p_2ln), logLik(p_3ln), logLik(p_4ln), logLik(p_5ln), logLik(p_6ln)),2)

Table_4[31,2:8] <- round(c(AIC((null_pln)), AIC(p_1ln), AIC(p_2ln), AIC(p_3ln), AIC(p_4ln), AIC(p_5ln), AIC(p_6ln)),2)

Table_4[is.na(Table_4)] <- ""

write.csv(Table_4, here::here("results", "TableS4.csv"), row.names = F)

kable(Table_4, col.names = c("","","","","","","",""))


```
### T4 Binomial
It does not seem to be possible to both weight and cluster using glm binomial. So the cluster has to be done after.

##### Team size weights

In R, this needs to be starting from the integer of 1 for the lowest.

```{r t3, warning = F}
df$nmodel_l <- round((1/df$nmodel)*112,0)

m_1a <- glm(neg10 ~ group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l)

m_2a <- glm(neg10 ~ group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_3a <- glm(neg10 ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_3a <- glm(neg10 ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_1b <- glm(neg10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_2b <- glm(neg10s ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_3b <- glm(neg10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l)

m_1c <- glm(pos10 ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_2c <- glm(pos10 ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_3c <- glm(pos10 ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_1d <- glm(pos10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_2d <- glm(pos10s ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

m_3d <- glm(pos10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_l) 

```

##### Ref score weights

again adjust for the lowest weight at integer 1

```{r t3rr, warning = F}

df$nmodel_lp <- round((df$pscore/df$nmodel)/(min(df$pscore/df$nmodel)), 0)

m_1ar <- glm(neg10 ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_2ar <- glm(neg10 ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_3ar <- glm(neg10 ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_1br <- glm(neg10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_2br <- glm(neg10s ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_3br <- glm(neg10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp)

m_1cr <- glm(pos10 ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_2cr <- glm(pos10 ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_3cr <- glm(pos10 ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_1dr <- glm(pos10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_2dr <- glm(pos10s ~ dindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

m_3dr <- glm(pos10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree),
             data = df,
             family = binomial(link = "logit"),
             weights = nmodel_lp) 

```


#### Build Table

```{r se3s}

Table_4a <- as.data.frame(matrix(nrow = 19, ncol = 5))

Table_4a[1,] <- c("", "(1)", "(2)", "(3)", "(3)")

Table_4a[2,] <- c("Dependent variable", "Mean sentiment", "Pro-imm. team", "Anti-imm. team", "Pro-imm. team")

Table_4a[,1] <- c("","Dependent vaiable", "A. Main regressions\nAME < 10th %", "", "AME < 10th % & sig.", "", "AME > 90th %", "", "AME > 90th % & sig.", "", "", "B. Weighted by referee score\nAME < 10th %",  "", "AME < 10th % & sig.", "", "AME > 90th %", "", "AME > 90th % & sig.", "")

# nu models weights
Table_4a[3,2:5] <- round(c(summary(margins(m_1a, variables = "proindex"))[,2],
                          summary(margins(m_2a, variables = "dindex"))[,2],
                          summary(margins(m_3a, variables = "group1"))[,2],
                          summary(margins(m_3a, variables = "group3"))[,2]),3)

Table_4a[5,2:5] <- round(c(summary(margins(m_1b, variables = "proindex"))[,2],
                          summary(margins(m_2b, variables = "dindex"))[,2],
                          summary(margins(m_3b, variables = "group1"))[,2],
                          summary(margins(m_3b, variables = "group3"))[,2]),3)

Table_4a[7,2:5] <- round(c(summary(margins(m_1c, variables = "proindex"))[,2],
                          summary(margins(m_2c, variables = "dindex"))[,2],
                          summary(margins(m_3c, variables = "group1"))[,2],
                          summary(margins(m_3c, variables = "group3"))[,2]),3)

Table_4a[9,2:5] <- round(c(summary(margins(m_1d, variables = "proindex"))[,2],
                          summary(margins(m_2d, variables = "dindex"))[,2],
                          summary(margins(m_3d, variables = "group1"))[,2],
                          summary(margins(m_3d, variables = "group3"))[,2]),3)
# peer review
Table_4a[12,2:5] <- round(c(summary(margins(m_1ar, variables = "proindex"))[,2],
                          summary(margins(m_2ar, variables = "dindex"))[,2],
                          summary(margins(m_3ar, variables = "group1"))[,2],
                          summary(margins(m_3ar, variables = "group3"))[,2]),3)

Table_4a[14,2:5] <- round(c(summary(margins(m_1br, variables = "proindex"))[,2],
                          summary(margins(m_2br, variables = "dindex"))[,2],
                          summary(margins(m_3br, variables = "group1"))[,2],
                          summary(margins(m_3br, variables = "group3"))[,2]),3)

Table_4a[16,2:5] <- round(c(summary(margins(m_1cr, variables = "proindex"))[,2],
                          summary(margins(m_2cr, variables = "dindex"))[,2],
                          summary(margins(m_3cr, variables = "group1"))[,2],
                          summary(margins(m_3cr, variables = "group3"))[,2]),3)

Table_4a[18,2:5] <- round(c(summary(margins(m_1dr, variables = "proindex"))[,2],
                          summary(margins(m_2dr, variables = "dindex"))[,2],
                          summary(margins(m_3dr, variables = "group1"))[,2],
                          summary(margins(m_3dr, variables = "group3"))[,2]),3)

# hack standard error as a proportion to the original based on the proportion of the standardized effect

# main models
Table_4a[4,2:5] <- round(c(
  unname(
  coeftest(m_1a, vcov. = vcovCL(m_1a, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1a, variables = "proindex"))[,2]
  / m_1a$coefficients[2]),
  unname(
  coeftest(m_2a, vcov. = vcovCL(m_2a, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2a, variables = "dindex"))[,2]
  / m_2a$coefficients[2]),
  unname(
  coeftest(m_3a, vcov. = vcovCL(m_3a, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3a, variables = "group1"))[,2]
  / m_3a$coefficients[2]),
  unname(
  coeftest(m_3a, vcov. = vcovCL(m_3a, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3a, variables = "group3"))[,2]
  / m_3a$coefficients[3])
),3)

Table_4a[6,2:5] <- round(c(
  unname(
  coeftest(m_1b, vcov. = vcovCL(m_1b, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1b, variables = "proindex"))[,2]
  / m_1b$coefficients[2]),
  unname(
  coeftest(m_2b, vcov. = vcovCL(m_2b, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2b, variables = "dindex"))[,2]
  / m_2b$coefficients[2]),
  unname(
  coeftest(m_3b, vcov. = vcovCL(m_3b, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3b, variables = "group1"))[,2]
  / m_3b$coefficients[2]),
  unname(
  coeftest(m_3b, vcov. = vcovCL(m_3b, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3b, variables = "group3"))[,2]
  / m_3b$coefficients[3])
),3)
  
Table_4a[8,2:5] <- round(c(
  unname(
  coeftest(m_1c, vcov. = vcovCL(m_1c, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1c, variables = "proindex"))[,2]
  / m_1c$coefficients[2]),
  unname(
  coeftest(m_2c, vcov. = vcovCL(m_2c, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2c, variables = "dindex"))[,2]
  / m_2c$coefficients[2]),
  unname(
  coeftest(m_3c, vcov. = vcovCL(m_3c, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3c, variables = "group1"))[,2]
  / m_3c$coefficients[2]),
  unname(
  coeftest(m_3c, vcov. = vcovCL(m_3c, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3c, variables = "group3"))[,2]
  / m_3c$coefficients[3])
),3)

Table_4a[10,2:5] <- round(c(
  unname(
  coeftest(m_1d, vcov. = vcovCL(m_1d, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1d, variables = "proindex"))[,2]
  / m_1d$coefficients[2]),
  unname(
  coeftest(m_2d, vcov. = vcovCL(m_2d, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2d, variables = "dindex"))[,2]
  / m_2d$coefficients[2]),
  unname(
  coeftest(m_3d, vcov. = vcovCL(m_3d, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3d, variables = "group1"))[,2]
  / m_3d$coefficients[2]),
  unname(
  coeftest(m_3d, vcov. = vcovCL(m_3d, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3d, variables = "group3"))[,2]
  / m_3d$coefficients[3])
),3)

# peer review models
Table_4a[13,2:5] <- round(c(
  unname(
  coeftest(m_1ar, vcov. = vcovCL(m_1ar, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1ar, variables = "proindex"))[,2]
  / m_1ar$coefficients[2]),
  unname(
  coeftest(m_2ar, vcov. = vcovCL(m_2ar, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2ar, variables = "dindex"))[,2]
  / m_2ar$coefficients[2]),
  unname(
  coeftest(m_3ar, vcov. = vcovCL(m_3ar, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3ar, variables = "group1"))[,2]
  / m_3ar$coefficients[2]),
  unname(
  coeftest(m_3ar, vcov. = vcovCL(m_3ar, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3ar, variables = "group3"))[,2]
  / m_3ar$coefficients[3])
),3)

Table_4a[15,2:5] <- round(c(
  unname(
  coeftest(m_1br, vcov. = vcovCL(m_1br, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1br, variables = "proindex"))[,2]
  / m_1br$coefficients[2]),
  unname(
  coeftest(m_2br, vcov. = vcovCL(m_2br, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2br, variables = "dindex"))[,2]
  / m_2br$coefficients[2]),
  unname(
  coeftest(m_3br, vcov. = vcovCL(m_3br, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3br, variables = "group1"))[,2]
  / m_3br$coefficients[2]),
  unname(
  coeftest(m_3br, vcov. = vcovCL(m_3br, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3br, variables = "group3"))[,2]
  / m_3br$coefficients[3])
),3)
  
Table_4a[17,2:5] <- round(c(
  unname(
  coeftest(m_1cr, vcov. = vcovCL(m_1cr, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1cr, variables = "proindex"))[,2]
  / m_1cr$coefficients[2]),
  unname(
  coeftest(m_2cr, vcov. = vcovCL(m_2cr, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2cr, variables = "dindex"))[,2]
  / m_2cr$coefficients[2]),
  unname(
  coeftest(m_3cr, vcov. = vcovCL(m_3cr, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3cr, variables = "group1"))[,2]
  / m_3cr$coefficients[2]),
  unname(
  coeftest(m_3cr, vcov. = vcovCL(m_3cr, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3cr, variables = "group3"))[,2]
  / m_3cr$coefficients[3])
),3)

Table_4a[19,2:5] <- round(c(
  unname(
  coeftest(m_1dr, vcov. = vcovCL(m_1dr, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_1dr, variables = "proindex"))[,2]
  / m_1dr$coefficients[2]),
  unname(
  coeftest(m_2dr, vcov. = vcovCL(m_2dr, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_2dr, variables = "dindex"))[,2]
  / m_2dr$coefficients[2]),
  unname(
  coeftest(m_3dr, vcov. = vcovCL(m_3dr, cluster = ~ df$u_teamid))[2, 2] 
  * summary(margins(m_3dr, variables = "group1"))[,2]
  / m_3d$coefficients[2]),
  unname(
  coeftest(m_3dr, vcov. = vcovCL(m_3dr, cluster = ~ df$u_teamid))[3, 2] 
  * summary(margins(m_3dr, variables = "group3"))[,2]
  / m_3d$coefficients[3])
),3)

kable(Table_4a, col.names = c("","","","",""))
```
### Models

```{r t4m}
df_p <- subset(df, !is.na(peer_N))

m4_1 <- lm.cluster(formula= peer_mean ~ proindex + t2 + t3 + stats_brw + topic_brw  + factor(mdegree), weights = df_p$peer_N/df_p$nmodel, cluster = "u_teamid", data = df_p)

m4_2 <- lm.cluster(formula= peer_mean ~ dindex + t2 + t3 + stats_brw + topic_brw  + factor(mdegree), weights = df_p$peer_N/df_p$nmodel, cluster = "u_teamid", data = df_p)

m4_3 <- lm.cluster(formula= peer_mean ~ group1 + group3 + t2 + t3 + stats_brw + topic_brw  + factor(mdegree), weights = df_p$peer_N/df_p$nmodel, cluster = "u_teamid", data = df_p)


df_p$peer_nmodel <- round((df_p$peer_N/df_p$nmodel)/min(df_p$peer_N/df_p$nmodel), 0)

m4_4 <- glm(quality2 ~ proindex + t2 + t3 + stats_brw + topic_brw  + factor(mdegree),
             data = df_p,
             family = binomial(link = "logit"),
             weights = peer_nmodel)

m4_5 <- glm(quality2 ~ dindex + t2 + t3 + stats_brw + topic_brw + factor(mdegree),
             data = df_p,
             family = binomial(link = "logit"),
             weights = peer_nmodel) 

# problem with too many parameters here, combine a few to ease in estimation
df_p <- df_p %>%
  mutate(mdegreex = case_when(mdegree == 1 ~ 30,
                              mdegree == 6 ~ 30,
                              mdegree == 2 ~ 30,
                              .default = mdegree))

m4_6 <- glm(quality2 ~ group1 + group3 + t2 + t3 + stats_brw + topic_brw + mdegreex,
             data = df_p,
             family = binomial(link = "logit"),
             weights = peer_nmodel)
```

#### Build

```{r t4b}

Table_4a <- as.data.frame(matrix(nrow = 17, ncol = 7))

Table_4a[,1] <- c("Variable:", "", "Mean pro-imm index", "", "Anti-imm, team", "", "Pro-imm, team", "", "Two-person team", "", "Three-person team", "", "Statistical skills", "", "Topic experience", "", "R-squared")

Table_4a[1,c(3,6)] <- c("Mean referee score", "High quality indicator")

Table_4a[2,2:7] <- c("(1)", "(2)", "(3)", "(1)", "(2)", "(3)")

# linear models
Table_4a[c(3,9,11,13,15),2] <- round(c(summary(m4_1)[2:6,1]),3)
Table_4a[c(4,10,12,14,16),2] <- round(c(summary(m4_1)[2:6,2]),3)

# logit clustered standard error hack
Table_4a[3:4,5] <- round(c(summary(margins(m4_4, variables = "proindex"))[,2],
                    unname(
                      coeftest(m4_4, vcov. = vcovCL(m4_4, cluster = ~ df_p$u_teamid))[2, 2] * summary(margins(m4_4, variables = "proindex"))[,2] / m4_4$coefficients[2])),3)

Table_4a[9:10,5] <- round(c(summary(margins(m4_4, variables = "t2"))[,2],
                    unname(
                      coeftest(m4_4, vcov. = vcovCL(m4_4, cluster = ~ df_p$u_teamid))[3, 2] * summary(margins(m4_4, variables = "t2"))[,2] / m4_4$coefficients[3])),3)

Table_4a[11:12,5] <- round(c(summary(margins(m4_4, variables = "t3"))[,2],
                    unname(
                      coeftest(m4_4, vcov. = vcovCL(m4_4, cluster = ~ df_p$u_teamid))[4, 2] * summary(margins(m4_4, variables = "t3"))[,2] / m4_4$coefficients[4])),3)

Table_4a[13:14,5] <- round(c(summary(margins(m4_4, variables = "stats_brw"))[,2],
                    unname(
                      coeftest(m4_4, vcov. = vcovCL(m4_4, cluster = ~ df_p$u_teamid))[5, 2] * summary(margins(m4_4, variables = "stats_brw"))[,2] / m4_4$coefficients[5])),3)

Table_4a[15:16,5] <- round(c(summary(margins(m4_4, variables = "topic_brw"))[,2],
                    unname(
                      coeftest(m4_4, vcov. = vcovCL(m4_4, cluster = ~ df_p$u_teamid))[6, 2] * summary(margins(m4_4, variables = "topic_brw"))[,2] / m4_4$coefficients[6])),3)

# linear
Table_4a[c(7,9,11,13,15),3] <- round(c(summary(m4_2)[2:6,1]),3)
Table_4a[c(8,10,12,14,16),3] <- round(c(summary(m4_2)[2:6,2]),3)

# logit
Table_4a[7:8,6] <- round(c(summary(margins(m4_5, variables = "dindex"))[,2],
                    unname(
                      coeftest(m4_5, vcov. = vcovCL(m4_5, cluster = ~ df_p$u_teamid))[2, 2] * summary(margins(m4_5, variables = "dindex"))[,2] / m4_5$coefficients[2])),3)

Table_4a[9:10,6] <- round(c(summary(margins(m4_5, variables = "t2"))[,2],
                    unname(
                      coeftest(m4_5, vcov. = vcovCL(m4_5, cluster = ~ df_p$u_teamid))[3, 2] * (summary(margins(m4_5, variables = "t2"))[,2] / m4_5$coefficients[3]))),3)

Table_4a[11:12,6] <- round(c(summary(margins(m4_5, variables = "t3"))[,2],
                    unname(
                      coeftest(m4_5, vcov. = vcovCL(m4_5, cluster = ~ df_p$u_teamid))[4, 2] * summary(margins(m4_5, variables = "t3"))[,2] / m4_5$coefficients[4])),3)

Table_4a[13:14,6] <- round(c(summary(margins(m4_5, variables = "stats_brw"))[,2],
                    unname(
                      coeftest(m4_5, vcov. = vcovCL(m4_5, cluster = ~ df_p$u_teamid))[5, 2] * summary(margins(m4_5, variables = "stats_brw"))[,2] / m4_5$coefficients[5])),3)

Table_4a[15:16,6] <- round(c(summary(margins(m4_5, variables = "topic_brw"))[,2],
                    unname(
                      coeftest(m4_5, vcov. = vcovCL(m4_5, cluster = ~ df_p$u_teamid))[6, 2] * summary(margins(m4_5, variables = "topic_brw"))[,2] / m4_5$coefficients[6])),3)

Table_4a[c(5,7,9,11,13,15),4] <- round(c(summary(m4_3)[2:7,1]),3)
Table_4a[c(6,8,10,12,14,16),4] <- round(c(summary(m4_3)[2:7,2]),3)

# logit
Table_4a[5:6,7] <- round(c(summary(margins(m4_6, variables = "group1"))[,2],
                    unname(
                      coeftest(m4_6, vcov. = vcovCL(m4_6, cluster = ~ df_p$u_teamid))[2, 2] * summary(margins(m4_6, variables = "group1"))[,2] / m4_6$coefficients[2])),3)

Table_4a[7:8,7] <- round(c(summary(margins(m4_6, variables = "group3"))[,2],
                    unname(
                      coeftest(m4_6, vcov. = vcovCL(m4_6, cluster = ~ df_p$u_teamid))[3, 2] * summary(margins(m4_6, variables = "group3"))[,2] / m4_6$coefficients[3])),3)

Table_4a[9:10,7] <- round(c(summary(margins(m4_6, variables = "t2"))[,2],
                    unname(
                      coeftest(m4_6, vcov. = vcovCL(m4_6, cluster = ~ df_p$u_teamid))[4, 2] * (summary(margins(m4_6, variables = "t2"))[,2] / m4_6$coefficients[4]))),3)

Table_4a[11:12,7] <- round(c(summary(margins(m4_6, variables = "t3"))[,2],
                    unname(
                      coeftest(m4_6, vcov. = vcovCL(m4_6, cluster = ~ df_p$u_teamid))[5, 2] * summary(margins(m4_6, variables = "t3"))[,2] / m4_6$coefficients[5])),3)

Table_4a[13:14,7] <- round(c(summary(margins(m4_6, variables = "stats_brw"))[,2],
                    unname(
                      coeftest(m4_6, vcov. = vcovCL(m4_6, cluster = ~ df_p$u_teamid))[6, 2] * summary(margins(m4_6, variables = "stats_brw"))[,2] / m4_6$coefficients[6])),3)

Table_4a[15:16,7] <- round(c(summary(margins(m4_6, variables = "topic_brw"))[,2],
                    unname(
                      coeftest(m4_6, vcov. = vcovCL(m4_6, cluster = ~ df_p$u_teamid))[7, 2] * summary(margins(m4_6, variables = "topic_brw"))[,2] / m4_6$coefficients[7])),3)

#for r-sqaured must calculate by hand
null_model <- glm(quality2 ~ 1, data = df_p, family = binomial(link = "logit"), weights = peer_nmodel)

Table_4a[17,2:7] <- round(c(r2ext(m4_1), r2ext(m4_1), r2ext(m4_3), 1 - (logLik(m4_4) / logLik(null_model)), 1 - (logLik(m4_5) / logLik(null_model)), 1 - (logLik(m4_6) / logLik(null_model))),3)

Table_4a[is.na(Table_4a)] <- ""
kable(Table_4a, col.names = c("", "", "", "", "", "", ""))
```

## Table 5. Neg extreme. Individual-model dyads

Individual level models

### Build Models


```{r t5}

m_1dn <- lm.cluster(formula=neg10s ~ indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_2dn <- lm.cluster(formula=neg10s ~ indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_3dn <- lm.cluster(formula=neg10s ~ indiv1 + indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_4dn <- lm.cluster(formula=neg10s ~ indiv1 + indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_5dn <- lm.cluster(formula=neg10s ~ att + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_6dn <- lm.cluster(formula=neg10s ~ att + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)


p_1dn <- lm.cluster(formula=neg10s ~ indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_2dn <- lm.cluster(formula=neg10s ~ indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_3dn <- lm.cluster(formula=neg10s ~ indiv1 + indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_4dn <- lm.cluster(formula=neg10s ~ indiv1 + indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_5dn <- lm.cluster(formula=neg10s ~ att + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_6dn <- lm.cluster(formula=neg10s ~ att + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

null_mdn <- lm.cluster(formula=neg10s ~ stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

null_pdn <- lm.cluster(formula=neg10s ~ stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

# re-run as lm's to get fit stats
source(here("code", "Sub", "t5_fit.R"))

#nobs(m_1ldn)
```

### Build Table

```{r t5r}

Table_5 <- as.data.frame(matrix(nrow = 32, ncol = 8))

Table_5[,1] <- c("Variable", "Anti-immigration team", "", "Pro-immigration team", "", "Statistical skills", "", "Topic experience", "", "Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC",  "R-squared", "", "Anti-immigration team", "", "Pro-immigration team", "",  "Statistical skills", "", "Topic experience", "","Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC", "R-squared")

Table_5[1,2:8] <- c("Null", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)")

#m_ models
Table_5[c(6,8),2] <- format(round(as.numeric(null_mdn$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_5[c(7,9),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_mdn)[2:3,2]),3), nsmall = 3))

Table_5[c(4,6,8),3] <- format(round(as.numeric(m_1dn$lm_res$coefficients[2:4]),3))
Table_5[c(5,7,9),3] <- sprintf("(%s)", format(round(as.numeric(summary(m_1dn)[2:4,2]),3), nsmall = 3))

Table_5[c(4,10,6,8),4] <- format(round(as.numeric(m_2dn$lm_res$coefficients[2:5]),3))
Table_5[c(5,11,7,9),4] <- sprintf("(%s)", format(round(as.numeric(summary(m_2dn)[2:5,2]),3), nsmall = 3))

Table_5[c(2,4,6,8),5] <- format(round(as.numeric(m_3dn$lm_res$coefficients[2:5]),3))
Table_5[c(3,5,7,9),5] <- sprintf("(%s)", format(round(as.numeric(summary(m_3dn)[2:5,2]),3), nsmall = 3))

Table_5[c(2,4,6,8,10),6] <- format(round(as.numeric(m_4dn$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_5[c(3,5,7,9,11),6] <- sprintf("(%s)", format(round(as.numeric(summary(m_4dn)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_5[c(12,6,8),7] <- format(round(as.numeric(m_5dn$lm_res$coefficients[2:4]), 3))
Table_5[c(13,7,9),7] <- sprintf("(%s)", format(round(as.numeric(summary(m_5dn)[2:4,2]),3), nsmall = 3))

Table_5[c(12,10,6,8),8] <- format(round(as.numeric(m_6dn$lm_res$coefficients[2:5]),3))
Table_5[c(13,11,7,9),8] <- sprintf("(%s)", format(round(as.numeric(summary(m_6dn)[2:5,2]),3), nsmall = 3))


Table_5[16,2:8] <- c(r2ext(null_mdn), r2ext(m_1dn), r2ext(m_2dn), r2ext(m_3dn), r2ext(m_4dn), r2ext(m_5dn), r2ext(m_6dn))

Table_5[14,2:8] <- round(c(logLik((null_mldn)), logLik(m_1ldn), logLik(m_2ldn), logLik(m_3ldn), logLik(m_4ldn), logLik(m_5ldn), logLik(m_6ldn)),2)

Table_5[15,2:8] <- round(c(AIC((null_mldn)), AIC(m_1ldn), AIC(m_2ldn), AIC(m_3ldn), AIC(m_4ldn), AIC(m_5ldn), AIC(m_6ldn)),2)

#p_ models
Table_5[c(22,24),2] <- format(round(as.numeric(null_pdn$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_5[c(23,25),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_pdn)[2:3,2]),3), nsmall = 3))

Table_5[c(20,22,24),3] <- format(round(as.numeric(p_1dn$lm_res$coefficients[2:4]),3))
Table_5[c(21,23,25),3] <- sprintf("(%s)", format(round(as.numeric(summary(p_1dn)[2:4,2]),3), nsmall = 3))

Table_5[c(20,26,22,24),4] <- format(round(as.numeric(p_2dn$lm_res$coefficients[2:5]),3))
Table_5[c(21,27,23,25),4] <- sprintf("(%s)", format(round(as.numeric(summary(p_2dn)[2:5,2]),3), nsmall = 3))

Table_5[c(18,20,22,24),5] <- format(round(as.numeric(p_3dn$lm_res$coefficients[2:5]),3))
Table_5[c(19,21,23,25),5] <- sprintf("(%s)", format(round(as.numeric(summary(p_3dn)[2:5,2]),3), nsmall = 3))

Table_5[c(18,20,22,24,26),6] <- format(round(as.numeric(p_4dn$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_5[c(19,21,23,25,27),6] <- sprintf("(%s)", format(round(as.numeric(summary(p_4dn)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_5[c(28,22,24),7] <- format(round(as.numeric(p_5dn$lm_res$coefficients[2:4]), 3))
Table_5[c(29,23,25),7] <- sprintf("(%s)", format(round(as.numeric(summary(p_5dn)[2:4,2]),3), nsmall = 3))

Table_5[c(28,26,22,24),8] <- format(round(as.numeric(p_6dn$lm_res$coefficients[2:5]),3))
Table_5[c(29,27,23,25),8] <- sprintf("(%s)", format(round(as.numeric(summary(p_6dn)[2:5,2]),3), nsmall = 3))

Table_5[32,2:8] <- c(r2ext(null_pdn), r2ext(p_1dn), r2ext(p_2dn), r2ext(p_3dn), r2ext(p_4dn), r2ext(p_5dn), r2ext(p_6dn))

Table_5[30,2:8] <- round(c(logLik((null_pldn)), logLik(p_1ldn), logLik(p_2ldn), logLik(p_3ldn), logLik(p_4ldn), logLik(p_5ldn), logLik(p_6ldn)),2)

Table_5[31,2:8] <- round(c(AIC((null_pldn)), AIC(p_1ldn), AIC(p_2ldn), AIC(p_3ldn), AIC(p_4ldn), AIC(p_5ldn), AIC(p_6ldn)),2)

Table_5[is.na(Table_5)] <- ""

write.csv(Table_5, here::here("results", "TableS5.csv"), row.names = F)

kable(Table_5, col.names = c("","","","","","","",""))


```


## Table 6. Pos extreme. Model-level

### Build Models

```{r t6}

m_1p <- lm.cluster(formula=pos10s ~ group1 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_2p <- lm.cluster(formula=pos10s ~ group1 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_3p <- lm.cluster(formula=pos10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_4p <- lm.cluster(formula=pos10s ~ group1 + group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_5p <- lm.cluster(formula=pos10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

m_6p <- lm.cluster(formula=pos10s ~ proindex + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)


p_1p <- lm.cluster(formula=pos10s ~ group1 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_2p <- lm.cluster(formula=pos10s ~ group1 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_3p <- lm.cluster(formula=pos10s ~ group1 + group3 + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_4p <- lm.cluster(formula=pos10s ~ group1 + group3 + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_5p <- lm.cluster(formula=pos10s ~ proindex + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

p_6p <- lm.cluster(formula=pos10s ~ proindex + pbelief + stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

null_mp <- lm.cluster(formula=pos10s ~ stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = 1/df$nmodel, cluster = "u_teamid", data = df)

null_pp <- lm.cluster(formula=pos10s ~ stats_brw + topic_brw + t2 + t3 + factor(mdegree), weights = df$pscore/df$nmodel, cluster = "u_teamid", data = df)

# re-run as lm's to get fit stats
source(here("code", "Sub", "t6_fit.R"))

```

### Build Table

```{r t6r}

Table_6 <- as.data.frame(matrix(nrow = 32, ncol = 8))

Table_6[,1] <- c("Variable", "Anti-immigration team", "", "Pro-immigration team", "", "Statistical skills", "", "Topic experience", "", "Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC",  "R-squared", "", "Anti-immigration team", "", "Pro-immigration team", "",  "Statistical skills", "", "Topic experience", "","Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC", "R-squared")

Table_6[1,2:8] <- c("Null", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)")

#m_ models
Table_6[c(6,8),2] <- format(round(as.numeric(null_mp$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_6[c(7,9),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_mp)[2:3,2]),3), nsmall = 3))

Table_6[c(2,6,8),3] <- format(round(as.numeric(m_1p$lm_res$coefficients[2:4]),3))
Table_6[c(3,7,9),3] <- sprintf("(%s)", format(round(as.numeric(summary(m_1p)[2:4,2]),3), nsmall = 3))

Table_6[c(2,10,6,8),4] <- format(round(as.numeric(m_2p$lm_res$coefficients[2:5]),3))
Table_6[c(3,11,7,9),4] <- sprintf("(%s)", format(round(as.numeric(summary(m_2p)[2:5,2]),3), nsmall = 3))

Table_6[c(2,4,6,8),5] <- format(round(as.numeric(m_3p$lm_res$coefficients[2:5]),3))
Table_6[c(3,5,7,9),5] <- sprintf("(%s)", format(round(as.numeric(summary(m_3p)[2:5,2]),3), nsmall = 3))

Table_6[c(2,4,6,8,10),6] <- format(round(as.numeric(m_4p$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_6[c(3,5,7,9,11),6] <- sprintf("(%s)", format(round(as.numeric(summary(m_4p)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_6[c(12,6,8),7] <- format(round(as.numeric(m_5p$lm_res$coefficients[2:4]), 3))
Table_6[c(13,7,9),7] <- sprintf("(%s)", format(round(as.numeric(summary(m_5p)[2:4,2]),3), nsmall = 3))

Table_6[c(12,10,6,8),8] <- format(round(as.numeric(m_6p$lm_res$coefficients[2:5]),3))
Table_6[c(13,11,7,9),8] <- sprintf("(%s)", format(round(as.numeric(summary(m_6p)[2:5,2]),3), nsmall = 3))


Table_6[16,2:8] <- c(r2ext(null_mp), r2ext(m_1p), r2ext(m_2p), r2ext(m_3p), r2ext(m_4p), r2ext(m_5p), r2ext(m_6p))

Table_6[14,2:8] <- round(c(logLik((null_mlp)), logLik(m_1lp), logLik(m_2lp), logLik(m_3lp), logLik(m_4lp), logLik(m_5lp), logLik(m_6lp)),2)

Table_6[15,2:8] <- round(c(AIC((null_mlp)), AIC(m_1lp), AIC(m_2lp), AIC(m_3lp), AIC(m_4lp), AIC(m_5lp), AIC(m_6lp)),2)

#p_ models
Table_6[c(22,24),2] <- format(round(as.numeric(null_pp$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_6[c(23,25),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_pp)[2:3,2]),3), nsmall = 3))

Table_6[c(18,22,24),3] <- format(round(as.numeric(p_1p$lm_res$coefficients[2:4]),3))
Table_6[c(19,23,25),3] <- sprintf("(%s)", format(round(as.numeric(summary(p_1p)[2:4,2]),3), nsmall = 3))

Table_6[c(18,26,22,24),4] <- format(round(as.numeric(p_2p$lm_res$coefficients[2:5]),3))
Table_6[c(19,27,23,25),4] <- sprintf("(%s)", format(round(as.numeric(summary(p_2p)[2:5,2]),3), nsmall = 3))

Table_6[c(18,20,22,24),5] <- format(round(as.numeric(p_3p$lm_res$coefficients[2:5]),3))
Table_6[c(19,21,23,25),5] <- sprintf("(%s)", format(round(as.numeric(summary(p_3p)[2:5,2]),3), nsmall = 3))

Table_6[c(18,20,22,24,26),6] <- format(round(as.numeric(p_4p$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_6[c(19,21,23,25,27),6] <- sprintf("(%s)", format(round(as.numeric(summary(p_4p)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_6[c(28,22,24),7] <- format(round(as.numeric(p_5p$lm_res$coefficients[2:4]), 3))
Table_6[c(29,23,25),7] <- sprintf("(%s)", format(round(as.numeric(summary(p_5p)[2:4,2]),3), nsmall = 3))

Table_6[c(28,26,22,24),8] <- format(round(as.numeric(p_6p$lm_res$coefficients[2:5]),3))
Table_6[c(29,27,23,25),8] <- sprintf("(%s)", format(round(as.numeric(summary(p_6p)[2:5,2]),3), nsmall = 3))

Table_6[32,2:8] <- c(r2ext(null_pp), r2ext(p_1p), r2ext(p_2p), r2ext(p_3p), r2ext(p_4p), r2ext(p_5p), r2ext(p_6p))

Table_6[30,2:8] <- round(c(logLik((null_plp)), logLik(p_1lp), logLik(p_2lp), logLik(p_3lp), logLik(p_4lp), logLik(p_5lp), logLik(p_6lp)),2)

Table_6[31,2:8] <- round(c(AIC((null_plp)), AIC(p_1lp), AIC(p_2lp), AIC(p_3lp), AIC(p_4lp), AIC(p_5lp), AIC(p_6lp)),2)

Table_6[is.na(Table_6)] <- ""

write.csv(Table_6, here::here("results", "TableS6.csv"), row.names = F)

kable(Table_6, col.names = c("","","","","","","",""))


```

## Table 7. Pos extreme. Individual-model dyads

### Build Models


```{r t7}

m_1dp <- lm.cluster(formula=pos10s ~ indiv1 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_2dp <- lm.cluster(formula=pos10s ~ indiv1 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_3dp <- lm.cluster(formula=pos10s ~ indiv1 + indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_4dp <- lm.cluster(formula=pos10s ~ indiv1 + indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_5dp <- lm.cluster(formula=pos10s ~ att + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

m_6dp <- lm.cluster(formula=pos10s ~ att + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)


p_1dp <- lm.cluster(formula=pos10s ~ indiv1 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_2dp <- lm.cluster(formula=pos10s ~ indiv1 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_3dp <- lm.cluster(formula=pos10s ~ indiv1 + indiv3 + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_4dp <- lm.cluster(formula=pos10s ~ indiv1 + indiv3 + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_5dp <- lm.cluster(formula=pos10s ~ att + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

p_6dp <- lm.cluster(formula=pos10s ~ att + pbelief + stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

null_mdp <- lm.cluster(formula=pos10s ~ stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight, cluster = "u_teamid", data = df_dyad)

null_pdp <- lm.cluster(formula=pos10s ~ stats_i + topic_i + t2 + t3 + factor(backgr_degree), weights = df_dyad$pweight*df_dyad$pscore, cluster = "u_teamid", data = df_dyad)

# re-run as lm's to get fit stats
source(here("code", "Sub", "t7_fit.R"))

#nobs(m_1ldp)
```

### Build Table

```{r t7r}

Table_7 <- as.data.frame(matrix(nrow = 32, ncol = 8))

Table_7[,1] <- c("Variable", "Anti-immigration team", "", "Pro-immigration team", "", "Statistical skills", "", "Topic experience", "", "Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC",  "R-squared", "", "Anti-immigration team", "", "Pro-immigration team", "",  "Statistical skills", "", "Topic experience", "","Hypothesis prior", "", "Pro-immigration index", "", "Log-Lik", "AIC", "R-squared")

Table_7[1,2:8] <- c("Null", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)")

#m_ models
Table_7[c(6,8),2] <- format(round(as.numeric(null_mdp$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_7[c(7,9),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_mdp)[2:3,2]),3), nsmall = 3))

Table_7[c(2,6,8),3] <- format(round(as.numeric(m_1dp$lm_res$coefficients[2:4]),3))
Table_7[c(3,7,9),3] <- sprintf("(%s)", format(round(as.numeric(summary(m_1dp)[2:4,2]),3), nsmall = 3))

Table_7[c(2,10,6,8),4] <- format(round(as.numeric(m_2dp$lm_res$coefficients[2:5]),3))
Table_7[c(3,11,7,9),4] <- sprintf("(%s)", format(round(as.numeric(summary(m_2dp)[2:5,2]),3), nsmall = 3))

Table_7[c(2,4,6,8),5] <- format(round(as.numeric(m_3dp$lm_res$coefficients[2:5]),3))
Table_7[c(3,5,7,9),5] <- sprintf("(%s)", format(round(as.numeric(summary(m_3dp)[2:5,2]),3), nsmall = 3))

Table_7[c(2,4,6,8,10),6] <- format(round(as.numeric(m_4dp$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_7[c(3,5,7,9,11),6] <- sprintf("(%s)", format(round(as.numeric(summary(m_4dp)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_7[c(12,6,8),7] <- format(round(as.numeric(m_5dp$lm_res$coefficients[2:4]), 3))
Table_7[c(13,7,9),7] <- sprintf("(%s)", format(round(as.numeric(summary(m_5dp)[2:4,2]),3), nsmall = 3))

Table_7[c(12,10,6,8),8] <- format(round(as.numeric(m_6dp$lm_res$coefficients[2:5]),3))
Table_7[c(13,11,7,9),8] <- sprintf("(%s)", format(round(as.numeric(summary(m_6dp)[2:5,2]),3), nsmall = 3))


Table_7[16,2:8] <- c(r2ext(null_mdp), r2ext(m_1dp), r2ext(m_2dp), r2ext(m_3dp), r2ext(m_4dp), r2ext(m_5dp), r2ext(m_6dp))

Table_7[14,2:8] <- round(c(logLik((null_mldp)), logLik(m_1ldp), logLik(m_2ldp), logLik(m_3ldp), logLik(m_4ldp), logLik(m_5ldp), logLik(m_6ldp)),2)

Table_7[15,2:8] <- round(c(AIC((null_mlp)), AIC(m_1ldp), AIC(m_2ldp), AIC(m_3ldp), AIC(m_4ldp), AIC(m_5ldp), AIC(m_6ldp)),2)

#p_ models
Table_7[c(22,24),2] <- format(round(as.numeric(null_pdp$lm_res$coefficients[2:3]),3), nsmall = 3)
Table_7[c(23,25),2] <- sprintf("(%s)", format(round(as.numeric(summary(null_pdp)[2:3,2]),3), nsmall = 3))

Table_7[c(18,22,24),3] <- format(round(as.numeric(p_1dn$lm_res$coefficients[2:4]),3))
Table_7[c(19,23,25),3] <- sprintf("(%s)", format(round(as.numeric(summary(p_1dn)[2:4,2]),3), nsmall = 3))

Table_7[c(18,26,22,24),4] <- format(round(as.numeric(p_2dp$lm_res$coefficients[2:5]),3))
Table_7[c(19,27,23,25),4] <- sprintf("(%s)", format(round(as.numeric(summary(p_2dp)[2:5,2]),3), nsmall = 3))

Table_7[c(18,20,22,24),5] <- format(round(as.numeric(p_3dp$lm_res$coefficients[2:5]),3))
Table_7[c(19,21,23,25),5] <- sprintf("(%s)", format(round(as.numeric(summary(p_3dp)[2:5,2]),3), nsmall = 3))

Table_7[c(18,20,22,24,26),6] <- format(round(as.numeric(p_4dp$lm_res$coefficients[c(2,3,5,6,4)]),3))
Table_7[c(19,21,23,25,27),6] <- sprintf("(%s)", format(round(as.numeric(summary(p_4dp)[c(2,3,5,6,4),2]),3), nsmall = 3))

Table_7[c(28,22,24),7] <- format(round(as.numeric(p_5dp$lm_res$coefficients[2:4]), 3))
Table_7[c(29,23,25),7] <- sprintf("(%s)", format(round(as.numeric(summary(p_5dp)[2:4,2]),3), nsmall = 3))

Table_7[c(28,26,22,24),8] <- format(round(as.numeric(p_6dp$lm_res$coefficients[2:5]),3))
Table_7[c(29,27,23,25),8] <- sprintf("(%s)", format(round(as.numeric(summary(p_6dp)[2:5,2]),3), nsmall = 3))

Table_7[32,2:8] <- c(r2ext(null_pdp), r2ext(p_1dp), r2ext(p_2dp), r2ext(p_3dp), r2ext(p_4dp), r2ext(p_5dp), r2ext(p_6dp))

Table_7[30,2:8] <- round(c(logLik((null_pldp)), logLik(p_1ldp), logLik(p_2ldp), logLik(p_3ldp), logLik(p_4ldp), logLik(p_5ldp), logLik(p_6ldp)),2)

Table_7[31,2:8] <- round(c(AIC((null_pldp)), AIC(p_1ldp), AIC(p_2ldp), AIC(p_3ldp), AIC(p_4ldp), AIC(p_5ldp), AIC(p_6ldp)),2)

Table_7[is.na(Table_7)] <- ""

write.csv(Table_7, here::here("results", "TableS7.csv"), row.names = F)

kable(Table_7, col.names = c("","","","","","","",""))


```















## Save Regression Estimates

```{r savereg}

reg_results <- save(m_1, m_3, p_1, p_3, m_1d, m_3d, p_1d, p_3d, m_1n, m_3n, p_1n, p_3n, m_1p, m_3p, p_1p, p_3p, file = here("results","reg_results.Rdata"))

```

## Citations

```{r cites}

packages %>%
  map(citation) %>%
  print(style = "text")

```

## Colophon

```{r colo}

sessionInfo()

```

